\documentclass[11pt]{article}

\usepackage{amssymb, enumitem, xcolor, titlesec, geometry, sectsty, hyperref}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{eso-pic}

\definecolor{SealGray}{HTML}{54585A}
\definecolor{CalPolyGreen}{HTML}{154734}

\newcommand\mybigskip{\bigskip}

\geometry{legalpaper, margin=15.15in}
\sectionfont{\fontsize{16}{16}\selectfont}

\color{SealGray}

\setlist[itemize]{itemsep=-1ex,topsep=0.5ex,parsep=1ex}
\setlength{\parindent}{0ex}
\setlength{\parskip}{0ex}

\titleformat*{\section}{\selectfont \large \bfseries \color{CalPolyGreen}}

\pagestyle{empty}


\begin{document}

~
~

\begin{center}
  {
	\fontsize{1.5cm}{1.5cm}
        \textcolor{CalPolyGreen}{\textbf{Conor Carroll}}
  }
  ~

  conorjamcar@gmail.com

\end{center}

~
~


\section*{\textcolor{CalPolyGreen}{Education}}
\begin{tabular}{llll}
        2020    & M.S.  & Mathematics           & Cal Poly, San Luis Obispo, CA \\
        2020    & B.S.  & Mathematics           & Cal Poly, San Luis Obispo, CA \\
        2020    & B.S.  & Computer Science      & Cal Poly, San Luis Obispo, CA \\
\end{tabular}

\section*{\textcolor{CalPolyGreen}{Employment}}

\begin{description}
    \item[Software Engineer]

	Google, Mountain View, CA.  07/20 -- present

	\begin{small}
	Building pipeline to monitor and improve Google's indisplay and video ad experiences.
	\end{small}

    \item[Research Assistant]

	Computer Science Dept, Cal Poly, San Luis Obispo, CA.  06/19 -- 03/20
	
	\begin{small}
	Used the GoogleMaps API to create a web-based tool for visualizing and analyzing a computer science collaboration network with Professor Zo\"{e} Wood.  Work included finding and classifying graph anomalies.
	\end{small}

    \item[Research Assistant]

	Math Dept, Cal Poly, San Luis Obispo, CA.  06/19 -- 07/20
	
	\begin{small}
	Hand selected to work in a paid summer research position under the direction
  of Professor Dana Paquin.  Our project focused on developing image processing techniques in the presence of large levels of impulse noise, resulting in a robust, multi-modal segmentation algorithm.

	\end{small}

    \item[Workshop Leader]

	Math Dept, Cal Poly, San Luis Obispo, CA.  06/19 -- 06/20

	\begin{small}
	Led discussion sections for students in Abstract Algebra (Group and Ring Theory).  Consisted of attending lecture, developing problem sets, and faciliating student discussion.
	\end{small}

    \item[Research Assistant]

	Math Dept, Cal Poly, San Luis Obispo, CA.  04/18 -- 04/19

	\begin{small}
	Worked with Professors Vincent Bonini and Erin Pearse to classify and extend curvature results on different classes of graphs.
	\end{small}

    \item[Workshop Leader]

	Academic Skills Center, Cal Poly, San Luis Obispo, CA.  04/17 -- 06/18

	\begin{small}
	Led discussion sections and developed problem sets for linear algebra and differential equations.
	\end{small}

    \item[Mechanical Engineering Intern]

	MOOG CSA Engineering, Mountain View, CA.  06/15 -- 12/17

\end{description}

\section*{\textcolor{CalPolyGreen}{Recognition}}

\begin{itemize}
        \item Bryant Russel Memorial Award - Cal Poly Math Dept., 2020
        \item Dean's List - Fall 2015, Winter 2016, Fall 2016, Fall 2017, Winter 2019
        \item Outstanding Student Poster Presentation - Joint Math Meeting, Baltimore 2019
        \item Outstanding Workshop Leader - Academic Skills Center, 2018
        \item George H. McMeen Scholarship - Cal Poly Mathematics Department, 2018

\end{itemize}


\section*{\textcolor{CalPolyGreen}{Skills}}

\begin{itemize}
        \item C++, C, Python, Java, SML
        \item Formal education in mathematics and computer science
        \item Public speaking
        \item Working proficiency in Spanish
        \item Design and analysis of algorithms
\end{itemize}


\end{document}
